Indian News Wordcloud
========================================================

This is a attempt to visualise what the news channels are talking about through a word cloud of the top stories in the national news section.

My first analysis is on **The Hindu**. 

[Here](http://www.thehindu.com/news/national/?service=rss) is the rss feed I am using.

This is all a learning experience for me. So, I will list all the resources I am using so that this might be an helpful example for someone else who is completely new to R. 

XML Parsing using the XML Package.

* A [Stackoverflow](http://stackoverflow.com/questions/13579996/how-to-create-an-r-data-frame-from-a-xml-file) Answer
* Tutorial on XML package.


```{r}

library(XML)
destFilename <- "hindu-rss.xml"
rssUrl <- "http://www.thehindu.com/news/national/?service=rss"
download.file(rssUrl, destFilename)
doc <- xmlParse(destFilename)
itemsDataFrame <- xmlToDataFrame(getNodeSet(doc,"//channel/item"))  
itemsDataFrame <- itemsDataFrame[c("title", "description")]
itemsDataFrame["title"] <- as.character(itemsDataFrame$title)
itemsDataFrame["description"] <- as.character(itemsDataFrame$description)

```

So we now have 2 string vectors. Now I want to make a word cloud of the text I have. I will use text mining package, tm and wordcloud package of R.

``` {r out.height = 800}
library(tm)
library(wordcloud)
news.corpus <- Corpus(DataframeSource(data.frame(itemsDataFrame)))
news.corpus <- tm_map(news.corpus, removePunctuation)
news.corpus <- tm_map(news.corpus, tolower)
news.corpus <- tm_map(news.corpus, function(x) removeWords(x, stopwords("english")))
news.tdm <- TermDocumentMatrix(news.corpus)
news.m <- as.matrix(news.tdm)
news.v <- sort(rowSums(news.m),decreasing=TRUE)
news.d <- data.frame(word = names(news.v),freq=news.v)
table(news.d$freq)
pal2 <- brewer.pal(8,"Dark2")

wordcloud(news.d$word,news.d$freq, scale=c(3,.2),min.freq=3,
          max.words=Inf, random.order=FALSE, rot.per=.15, colors=pal2)

```

I want to iterate over several news websites. Hence this is still under development. 
